My title\thanks{Code and data are available at: LINK.}

### 2024-03-19 paper/paper.tex
Removed the following code for table.
```{r}

library(knitr)
library(kableExtra)

# Define the list
dflist <- list(variables = c("All Americans", "Race", "Gender", "Political Affiliation", "Level of Education"),
               observations = c("All the following groups", "Self-identified race of participants", "Male/Female", "Democrat/Republican/Other", "College Degree or Higher/Highschool Diploma/No Highschool Diploma")
)

# Convert the list to a data frame
df <- as.data.frame(dflist)

# Display the data frame as a table with kableExtra
kbl(df) %>%
  kable_classic(full_width = FALSE, html_fon

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, breakable, boxrule=0pt, sharp corners, borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden]}{\end{tcolorbox}}\fi

>>>>

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, boxrule=0pt, interior hidden, sharp corners, breakable, enhanced, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi
